### 2021-09-15 paper/localpsf.tex
change bold package. Use G, F for greens functions

for arbitrary functions $u$ and $v$. After discretization (see Appendix \ref{app:discretized_operations}), $\Aop$ becomes a dense matrix, $\mathbf{A}$, that is typically too large to be built and stored. This property is called ``matrix-free'' because at the discrete level it means that one can perform matrix-vector products of $\mathbf{A}$ and $\mathbf{A}^T$ with arbitrary vectors, but one cannot easily\footnote{One could compute $\mathbf{v} = \mathbf{A}\mathbf{e}_j$, where $\mathbf{e}_j=(0,\dots,0,1,0,\dots,0)$ is the unit vector which has $j^\text{th}$ component equal to one and all other components equal to zero, then extract $\mathbf{A}_{ij} = \mathbf{v}_i$. However, this process is wasteful because one computes the entire vector $\mathbf{v}$, then discards all but one component.} access matrix entries $\mathbf{A}_{ij}$. In applications, applying $\mathbf{A}$ to a vector may involve iteratively solving a large linear system, timestepping, or performing some other nontrivial computational procedure. For example, in reduced space approaches to PDE-constrained optimization and inverse problems, Hessian information is available only through the application of the Hessian to vectors, and one such Hessian application requires solving two PDEs \cite{HESSIANADJOINT}. 

@@

Because of the non-negative kernel property, for each $x \in \Omega$, the impulse response $\impulseresponse_x$ is a non-negative function $y \mapsto \impulseresponse_x(y)$. Hence, $\impulseresponse_x$ is a scaled probability distribution. Let $\spatialvol(x) := \int_\Omega \impulseresponse_x(y) dy$ denote the scaling factor, let $\widehat{\impulseresponse}_x := \impulseresponse_x / \spatialvol(x)$ denote the normalized version of $\impulseresponse_x$, and let $\spatialmean(x)$ and $\spatialcov(x)$ denote the mean and covariance of $\widehat{\impulseresponse}_x$, respectively. We make the approximation that the support of $\impulseresponse_x$ is contained within the ellipsoid
\begin{equation}
	\label{eq:support_ellipsoid}
	E_x := \{x' \in \Omega: (x' - \spatialmean(x))^T \spatialcov(x)^{-1} (x' - \spatialmean(x)) \le \tau^2\},
\end{equation}
where $\tau$ is a fixed constant. The ellipsoid $E_x$ is the set of points within $\tau$ standard deviations from the mean of the Gaussian distribution with mean $\spatialmean(x)$ and covariance $\spatialcov(x)$, i.e., the Gaussian distribution which has the same mean and covariance as $\widehat{\impulseresponse}_x$ (see Figure FIG). The quantity $\tau$ is a parameter that must be chosen by the user of the algorithm. The larger $\tau$ is, the larger the ellipsoid $E_x$ is, and the more conservative the estimate is for the support of $\impulseresponse_x$. However, the cost of our algorithm will depend on how many non-overlapping ellipsoids $E_x$ we can ``pack'' in the domain $\Omega$ (more ellipsoids $\implies$ lower cost), and choosing a larger value of $\tau$ means that fewer ellipsoids will fit in $\Omega$. We find that $\tau=3$ yields a reasonable balance between these competing interests, and use $\tau=3$ in our numerical results. The fraction of the ``mass'' of $\impulseresponse_x$ residing outside of $E_x$ is less than $1/\tau^2$ by Chebyshev's inequality, though this bound is conservative and typically far less mass resides in this region.

@@

We may efficiently solve optimization problem \eqref{eq:wi_optimization_problem_generic} via the following procedure:
\begin{enumerate}
	\item For each sample point $x_i$, we compute a function $\firstgreens_i$ by solving the following Neumann Poisson problem:
	\begin{equation}
		\label{eq:psi_eq}
		\begin{cases}
			\Delta \firstgreens_i = \delta_{x_i} - 1/|\Omega|, & \text{in }\Omega, \\
			\nu \cdot \nabla \firstgreens_i = 0 & \text{on } \partial \Omega,
		\end{cases}
	\end{equation}
	with condition $\int_\Omega \firstgreens_i(x) dx = 0$. Here $\delta_{x_i}$ is the point source centered at $x_i$, $|\Omega|$ is the measure of the domain $\Omega$, and $\nu$ is the normal vector to $\partial \Omega$.
	\item For each function $\firstgreens_i$, we compute a function $\secondgreens_i$ by solving another Neumann Poisson problem:
	\begin{equation}
		\label{eq:theta_eq}
		\begin{cases}
			\Delta \secondgreens_i = \firstgreens_i, & \text{in }\Omega, \\
			\nu \cdot \nabla \secondgreens_i = 0 & \text{on } \partial \Omega,
		\end{cases}
	\end{equation}
	with condition $\int_\Omega \secondgreens_i(x) dx = 0$.
	\item The solution to optimization problem \eqref{eq:wi_optimization_problem_generic}, which we denote by $v_*$, is formed as follows:
	\begin{equation}
		\label{eq:optimal_v}
		v_*(x) := \beta + \sum_{i=1}^\convrank c_i \secondgreens_i(x),
	\end{equation}
	where the constants $c_i \in \mathbb{R}$, $i=1,\dots,\convrank$, and $\beta \in \mathbb{R}$ are the solution to the following linear system:
	\begin{equation}
		\label{eq:interpolation_linear_system}
		\begin{bmatrix}
			\pointinteractionmatrix & \mathbf{1} \\ \mathbf{1}^T & 0
		\end{bmatrix}
		\begin{bmatrix}
			\mathbf{c} \\ \beta
		\end{bmatrix}
		=
		\begin{bmatrix}
			\mathbf{\interpolatedvalues} \\ 0
		\end{bmatrix}.
	\end{equation}
	Here $\mathbf{c} \in \mathbb{R}^\convrank$ is the vector with $i$th component $c_i$, $\mathbf{1} \in \mathbf{R}^\convrank$ is the column vector of all ones, $\mathbf{\interpolatedvalues} \in \mathbb{R}^\convrank$ is the vector with $i$th component $\interpolatedvalues_i$, and $\pointinteractionmatrix \in \mathbb{R}^{\convrank \times \convrank}$ is the matrix with entries given by
	\begin{equation}
		\label{eq:S_matrix}
		\pointinteractionmatrix_{ij} := \left( \firstgreens_i, \firstgreens_j \right)_{L^2(\Omega)}.
	\end{equation}
\end{enumerate}
Linear system \eqref{eq:interpolation_linear_system} is the KKT system that arises if one solves optimization problem \eqref{eq:wi_optimization_problem_generic} on the $\convrank+1$-dimensional subspace of $H^2_N(\Omega)$ spanned by the functions $\secondgreens_i$, $i=1,\dots,\convrank$, and the constant function $C(x)=1$. In Theorem \ref{thm:wi_no_breakdown}, we prove that this procedure does not break down, and in Theorem \ref{thm:wi_alg_is_correct}, we prove that the function $v_*$ produced by this procedure is the solution to optimization problem \eqref{eq:wi_optimization_problem_generic} on $H^2_N(\Omega)$.

@@

\begin{thm}[Procedure for computing $v_*$ does not break down]
	\label{thm:wi_no_breakdown}
	If all the sample points $x_i$, $i=1,\dots,\convrank$, are distinct, then PDE \eqref{eq:psi_eq} is uniquely solvable for $\firstgreens_i$, PDE \eqref{eq:theta_eq} is uniquely solvable for $\secondgreens_i$, and linear system \eqref{eq:interpolation_linear_system} is uniquely solvable for $\mathbf{c}$ and $\beta$. That is, the procedure for computing $v_*$ does not break down. Furthermore, $v_* \in H^2_N(\Omega)$.
\end{thm}

@@

	Using the definition of $\pointinteractionmatrix$ and basic linear algebra, it is straightforward to show that if $\pointinteractionmatrix$ were singular, there would exist constants $a_1, a_2, \dots a_\convrank$, which are not all zero, such that
	\begin{equation*}
		0 = a_1 \firstgreens_1 + a_2 \firstgreens_2 + \dots a_\convrank \firstgreens_\convrank.
	\end{equation*}
	Applying the Laplacian to this equation yields
	\begin{equation*}
		0 = a_1 \delta_{x_1} + a_2 \delta_{x_2} + \dots a_\convrank \delta_{x_\convrank} - \left(\sum_{i=1}^\convrank a_i\right)\bigg/|\Omega|,
	\end{equation*}
	which is impossible because a nonzero linear combination of delta distributions at different points cannot equal a constant function. Thus we must conclude that $\pointinteractionmatrix$ is non-singular. By block matrix factorization, non-singularity of $\pointinteractionmatrix$ implies that linear system \eqref{eq:interpolation_linear_system} is uniquely solvable for $\mathbf{c}$ and $\beta$.

@@

	\paragraph{Feasibility} To show that $v_*$ is feasible (i.e., $v_* \in X$), we must show that $v_*(x_i) = \interpolatedvalues_i$ for $i=1,\dots,\convrank$. We have
	\begin{align*}
		v_*(x_i) &= \beta + \sum_{j=1}^\convrank c_j \secondgreens_j(x_i) \\
		&= \beta + \sum_{j=1}^\convrank c_j \left(\firstgreens_i, \Delta \secondgreens_j\right)_{L^2(\Omega)} + \avg\left(\secondgreens_j\right) \\
		&= \beta + \sum_{j=1}^\convrank c_j \left(\firstgreens_i, \firstgreens_j\right)_{L^2(\Omega)} \\
		&= \beta + \sum_{j=1}^\convrank c_j \pointinteractionmatrix_{ij}
	\end{align*}
	In the first line we used the definition of $v_*$ in \eqref{eq:optimal_v}. In the second line we used Lemma \ref{lem:psi_delta_eval}. In the third line we used the facts that, by construction, $\Delta \secondgreens_j = \firstgreens_j$ and $\int_\Omega \secondgreens_j(x) dx = 0$. In the fourth line we used the definition of $\pointinteractionmatrix$ in \eqref{eq:S_matrix}. Hence the condition $v_*(x_i) = \interpolatedvalues_i$ for $i=1,\dots,\convrank$ may be written in matrix form as
	\begin{equation*}
		\pointinteractionmatrix \mathbf{c} + \beta \mathbf{1} = \mathbf{\interpolatedvalues},
	\end{equation*}
	and this must hold because it is the first block row of system \eqref{eq:interpolation_linear_system} which is solved to compute $\mathbf{c}$ and $\beta$. So $v_* \in X$.

@@

	\paragraph{Variational equation} To show that $v_*$ satiafies variational equation \eqref{eq:variational_up}, notice that
	\begin{align*}
		(\Delta v_*, \Delta p)_{L^2(\Omega)} =& \sum_{i=1}^\convrank c_i(\Delta \secondgreens_i, \Delta p)_{L^2(\Omega)} \\
		=& \sum_{i=1}^\convrank c_i \left(p(x_i) - \avg\left(p\right)\right) \\
		=& -\avg\left(p\right) \sum_{i=1}^\convrank c_i. 
	\end{align*}
	In the first line we used the definition of $\secondgreens_i$ and the fact that the Laplacian of a constant is zero. In the second line we used Lemma \ref{lem:psi_delta_eval}. In the third line we used the fact that $p(x_i)=0$ because $p \in X_0$. Hence variational equation \eqref{eq:variational_up} holds if $\sum_{i=1}^\convrank c_i = 0$, which may be written in matrix form as $\mathbf{1}^T \mathbf{c} = 0$. This must hold because it is the second block row in system \eqref{eq:interpolation_linear_system}.
\end{proof}

@@

		\For{$i=1,2,\dots,\convrank$}{
			Solve the linear system
			\begin{equation*}
			\begin{bmatrix}
			\pointinteractionmatrix & \mathbf{1} \\ \mathbf{1}^T & 0
			\end{bmatrix}
			\begin{bmatrix}
			\mathbf{c}^{(i)} \\ \beta^{(i)}
			\end{bmatrix}
			=
			\begin{bmatrix}
			\mathbf{e}^{(i)} \\ 0
			\end{bmatrix}.
			\end{equation*}
			for $\mathbf{c}^{(i)}=(c_1^{(i)}, c_2^{(i)}, \dots, c_\convrank^{(i)})$ and $\beta^{(i)}$. Here $\mathbf{1} = (1,1,\dots,1) \in \mathbb{R}^\convrank$, and $\mathbf{e}^{(i)} = (0,\dots,0,1,0,\dots,0)\in \mathbb{R}^\convrank$ is the unit vector with $i^\text{th}$ component equal to one and all other components equal to zero.

			Form the weighting function $w_i$ given by
			\begin{equation*}
			w_i(x) = \beta^{(i)} + \sum_{k=1}^\convrank c_k^{(i)} \secondgreens_k(x).
			\end{equation*}

@@

Replacing $\Aker$ with $\AkerPcMesh$ within the definition of $\Aop$ in \eqref{eq:kernel_representation} yields the following operator approximation, $\AopPcMesh$:
\begin{equation}
	\label{eq:kernel_representation_pcmesh}
	(\AopPcMesh u)(v) := \int_\Omega \int_\Omega v(y) \AkerPcMesh(y,x) u(x) dx dy.
\end{equation}
While $\AopPcMesh$ is well-defined as a mapping $L^2(\Omega) \rightarrow L^2(\Omega)'$, we are interested in the restriction of $\AopPcMesh$ to functions in the finite element space. That is, $\AopPcMesh : V_h \rightarrow V_h'$. Let $u_h \in V_h$ and $v_h \in V_h$, and let $\mathbf{u}$ and $\mathbf{v}$ be the coefficient vectors for $u_h$ and $v_h$, respectively, with respect to the finite element basis $\febasis_1, \dots, \febasis_\fedim$. I.e., 
\begin{equation}
	\label{eq:fem_coeff_basis}
	u_h(x) = \sum_{i=1}^\fedim \mathbf{u}_i \febasis_i(x),
\end{equation}
and similar for $v_h$. Further, let $\mathbf{M} \in \mathbb{R}^{\fedim \times \fedim}$ be the finite element mass matrix, and let $\AkerPcMat \in \mathbb{R}^{\fedim \times \fedim}$ be following matrix of approximate kernel entries:
\begin{equation}
	\label{eq:Akerpcmat_entries}
	\left(\AkerPcMat\right)_{ij} := \AkerPcMesh(p_i, p_j).
\end{equation}
Using \eqref{eq:defn_of_Akerpcmesh}, \eqref{eq:kernel_representation_pcmesh}, \eqref{eq:fem_coeff_basis}, and \eqref{eq:Akerpcmat_entries}, the definition of the mass matrix, and performing algebraic manipulations, it is straightforward but tedious to show that
\begin{equation*}
	\left(\AopPcMesh u_h \right)(v_h) = \mathbf{v}^T \mathbf{M} \AkerPcMat \mathbf{M} \mathbf{u}.
\end{equation*}
The finite element matrix representation of $\AopPcMesh$, which we denote by $\AmatPc$, is therefore given by
\begin{equation}
	\label{eq:Amatpc_defn}
	\AmatPc := \mathbf{M} \AkerPcMat \mathbf{M}.
\end{equation}

@@

We form an H-matrix representation of $\AmatPc$ by converting $\AkerPcMat$ and $\mathbf{M}$ to H-matrix format, then using fast H-matrix methods to multiply these matrices according to \eqref{eq:Amatpc_defn}. Once $\AmatPc$ is in H-matrix format, useful matrix operations such as matrix-vector products, matrix-matrix addition, matrix-matrix multiplication, and matrix inversion may be performed using fast scalable H-matrix methods \cite{BORMHACKBUSCHBOOK}. We use H1 matrices in our numerical results, but any of the other H-matrix formats (such as H2, HODLR, HSS, HBS, and others \cite{HMATRIX}) could be used instead. For more details on H-matrices, we recommend \cite{HMATRIXGOOD}.

We convert $\AkerPcMat$ into H1 matrix format using the standard geometrical clustering/adaptive cross method implemented within the HLIBpro software package \cite{HLIBPRO}. Although $\AkerPcMat$ is a dense $\fedim \times \fedim$ matrix, constructing the H-matrix approximation of $\AkerPcMat$ only requires evaluation of $O(\hmatrixrank^2 \fedim \log \fedim)$ entries of $\AkerPc$, and these entries are computed via the formula in Equation \eqref{eq:eval_y_x}. Here $\hmatrixrank$ is the rank of the highest-rank block in the H-matrix. A dense representation of $\AkerPcMat$ is never formed. We describe this H-matrix construction process in detail in Appendix \ref{app:h_matrix}. We convert $\mathbf{M}$ to H-matrix format using standard H-matrix methods for sparse matrices implemented within HLIBpro, using the same recursive block partitioning structure as was used for $\AkerPcMat$.

@@

After reordering the rows and columns of $\AkerPcMat$ via the depth-first ordering described above, we partition the reordered version of $\AkerPcMat$ into a tree of $2 \times 2$ block matrices recursively. We use a geometric admissibility condition (discussed below) to decide which blocks to subdivide, and use the cluster trees for the rows and columns to determine how to subdivide those blocks. For the first stage of subdivision, let $r_1$ and $r_2$ be the children row clusters for the root of the row cluster tree, let $c_1$ and $c_2$ be the children column clusters for the root of the column cluster tree. The matrix $\AkerPcMat$ is partitioned into blocks as follows:
\begin{equation*}
	\begin{bmatrix}
		\left(\AkerPcMat\right)_{11} & \left(\AkerPcMat\right)_{12} \\
		\left(\AkerPcMat\right)_{21} & \left(\AkerPcMat\right)_{22},
	\end{bmatrix}
\end{equation*}
where $\left(\AkerPcMat\right)_{11}$ denotes the block of $\AkerPcMat$ with rows $r_1$ and columns $c_1$, $\left(\AkerPcMat\right)_{12}$ denotes the block of $\AkerPcMat$ with rows $r_1$ and columns $c_2$, and so on for $\left(\AkerPcMat\right)_{21}$ and $\left(\AkerPcMat\right)_{22}$.

>>>>

for arbitrary functions $u$ and $v$. After discretization (see Appendix \ref{app:discretized_operations}), $\Aop$ becomes a dense matrix, $\bm{A}$, that is typically too large to be built and stored. This property is called ``matrix-free'' because at the discrete level it means that one can perform matrix-vector products of $\bm{A}$ and $\bm{A}^T$ with arbitrary vectors, but one cannot easily\footnote{One could compute $\bm{v} = \bm{A}\bm{e}_j$, where $\bm{e}_j=(0,\dots,0,1,0,\dots,0)$ is the unit vector which has $j^\text{th}$ component equal to one and all other components equal to zero, then extract $\bm{A}_{ij} = \bm{v}_i$. However, this process is wasteful because one computes the entire vector $\bm{v}$, then discards all but one component.} access matrix entries $\bm{A}_{ij}$. In applications, applying $\bm{A}$ to a vector may involve iteratively solving a large linear system, timestepping, or performing some other nontrivial computational procedure. For example, in reduced space approaches to PDE-constrained optimization and inverse problems, Hessian information is available only through the application of the Hessian to vectors, and one such Hessian application requires solving two PDEs \cite{HESSIANADJOINT}. 

@@

Because of the non-negative kernel property, for each $x \in \Omega$, the impulse response $\impulseresponse_x$ is a non-negative function $y \mapsto \impulseresponse_x(y)$. Hence, $\impulseresponse_x$ is a scaled probability distribution. Let $\spatialvol(x) := \int_\Omega \impulseresponse_x(y) dy$ denote the scaling factor (the ``volume'' of $\impulseresponse_x$), let $\widehat{\impulseresponse}_x := \impulseresponse_x / \spatialvol(x)$ denote the normalized version of $\impulseresponse_x$, and let $\spatialmean(x)$ and $\spatialcov(x)$ denote the mean and covariance of $\widehat{\impulseresponse}_x$, respectively. We make the approximation that the support of $\impulseresponse_x$ is contained within the ellipsoid
\begin{equation}
	\label{eq:support_ellipsoid}
	E_x := \{x' \in \Omega: (x' - \spatialmean(x))^T \spatialcov(x)^{-1} (x' - \spatialmean(x)) \le \tau^2\},
\end{equation}
where $\tau$ is a fixed constant. The ellipsoid $E_x$ is the set of points within $\tau$ standard deviations from the mean of the Gaussian distribution with mean $\spatialmean(x)$ and covariance $\spatialcov(x)$, i.e., the Gaussian distribution which has the same mean and covariance as $\widehat{\impulseresponse}_x$ (see Figure FIG). The quantity $\tau$ is a parameter that must be chosen by the user of the algorithm. The larger $\tau$ is, the larger the ellipsoid $E_x$ is, and the more conservative the estimate is for the support of $\impulseresponse_x$. However, the cost of our algorithm will depend on how many non-overlapping ellipsoids $E_x$ we can ``pack'' in the domain $\Omega$ (more ellipsoids $\implies$ lower cost), and choosing a larger value of $\tau$ means that fewer ellipsoids will fit in $\Omega$. We find that $\tau=3$ yields a reasonable balance between these competing interests, and use $\tau=3$ in our numerical results. The fraction of the ``mass'' of $\impulseresponse_x$ residing outside of $E_x$ is less than $1/\tau^2$ by Chebyshev's inequality, though this bound is conservative and typically far less mass resides in this region.

@@

We may efficiently solve optimization problem \eqref{eq:wi_optimization_problem_generic} via the following procedure:
\begin{enumerate}
	\item For each sample point $x_i$, we compute a function $\firstgreens_i$ by solving the following Neumann Poisson problem:
	\begin{equation}
		\label{eq:psi_eq}
		\begin{cases}
			\Delta \firstgreens_i = \delta_{x_i} - 1/|\Omega|, & \text{in }\Omega, \\
			\nu \cdot \nabla \firstgreens_i = 0 & \text{on } \partial \Omega,
		\end{cases}
	\end{equation}
	with condition $\int_\Omega \firstgreens_i(x) dx = 0$. Here $\delta_{x_i}$ is the point source centered at $x_i$, $|\Omega|$ is the measure of the domain $\Omega$, and $\nu$ is the normal vector to $\partial \Omega$.
	\item For each function $\firstgreens_i$, we compute a function $\secondgreens_i$ by solving another Neumann Poisson problem:
	\begin{equation}
		\label{eq:theta_eq}
		\begin{cases}
			\Delta \secondgreens_i = \firstgreens_i, & \text{in }\Omega, \\
			\nu \cdot \nabla \secondgreens_i = 0 & \text{on } \partial \Omega,
		\end{cases}
	\end{equation}
	with condition $\int_\Omega \secondgreens_i(x) dx = 0$.
	\item The solution to optimization problem \eqref{eq:wi_optimization_problem_generic}, which we denote by $v_*$, is formed as follows:
	\begin{equation}
		\label{eq:optimal_v}
		v_*(x) := \constcoeff + \sum_{i=1}^\convrank \secondgreenscoeff_i \secondgreens_i(x),
	\end{equation}
	where the constants $\secondgreenscoeff_i \in \mathbb{R}$, $i=1,\dots,\convrank$, and $\constcoeff \in \mathbb{R}$ are the solution to the following linear system:
	\begin{equation}
		\label{eq:interpolation_linear_system}
		\begin{bmatrix}
			\pointinteractionmatrix & \bm{1} \\ \bm{1}^T & 0
		\end{bmatrix}
		\begin{bmatrix}
			\bm{\secondgreenscoeff} \\ \constcoeff
		\end{bmatrix}
		=
		\begin{bmatrix}
			\bm{\interpolatedvalues} \\ 0
		\end{bmatrix}.
	\end{equation}
	Here $\bm{\secondgreenscoeff} \in \mathbb{R}^\convrank$ is the vector with $i$th component $\secondgreenscoeff_i$, $\bm{1} \in \bm{R}^\convrank$ is the column vector of all ones, $\bm{\interpolatedvalues} \in \mathbb{R}^\convrank$ is the vector with $i$th component $\interpolatedvalues_i$, and $\pointinteractionmatrix \in \mathbb{R}^{\convrank \times \convrank}$ is the matrix with entries given by
	\begin{equation}
		\label{eq:S_matrix}
		\pointinteractionmatrix_{ij} := \left( \firstgreens_i, \firstgreens_j \right)_{L^2(\Omega)}.
	\end{equation}
\end{enumerate}
Linear system \eqref{eq:interpolation_linear_system} is the KKT system that arises if one solves optimization problem \eqref{eq:wi_optimization_problem_generic} on the $\convrank+1$-dimensional subspace of $H^2_N(\Omega)$ spanned by the functions $\secondgreens_i$, $i=1,\dots,\convrank$, and the constant function $C(x)=1$. In Theorem \ref{thm:wi_no_breakdown}, we prove that this procedure does not break down, and in Theorem \ref{thm:wi_alg_is_correct}, we prove that the function $v_*$ produced by this procedure is the solution to optimization problem \eqref{eq:wi_optimization_problem_generic} on $H^2_N(\Omega)$.

@@

\begin{thm}[Procedure for computing $v_*$ does not break down]
	\label{thm:wi_no_breakdown}
	If all the sample points $x_i$, $i=1,\dots,\convrank$, are distinct, then PDE \eqref{eq:psi_eq} is uniquely solvable for $\firstgreens_i$, PDE \eqref{eq:theta_eq} is uniquely solvable for $\secondgreens_i$, and linear system \eqref{eq:interpolation_linear_system} is uniquely solvable for $\bm{\secondgreenscoeff}$ and $\constcoeff$. That is, the procedure for computing $v_*$ does not break down. Furthermore, $v_* \in H^2_N(\Omega)$.
\end{thm}

@@

	Using the definition of $\pointinteractionmatrix$ and basic linear algebra, it is straightforward to show that if $\pointinteractionmatrix$ were singular, there would exist constants $a_1, a_2, \dots a_\convrank$, which are not all zero, such that
	\begin{equation*}
		0 = a_1 \firstgreens_1 + a_2 \firstgreens_2 + \dots a_\convrank \firstgreens_\convrank.
	\end{equation*}
	Applying the Laplacian to this equation yields
	\begin{equation*}
		0 = a_1 \delta_{x_1} + a_2 \delta_{x_2} + \dots a_\convrank \delta_{x_\convrank} - \left(\sum_{i=1}^\convrank a_i\right)\bigg/|\Omega|,
	\end{equation*}
	which is impossible because a nonzero linear combination of delta distributions at different points cannot equal a constant function. Thus we must conclude that $\pointinteractionmatrix$ is non-singular. By block matrix factorization, non-singularity of $\pointinteractionmatrix$ implies that linear system \eqref{eq:interpolation_linear_system} is uniquely solvable for $\bm{\secondgreenscoeff}$ and $\constcoeff$.

@@

	\paragraph{Feasibility} To show that $v_*$ is feasible (i.e., $v_* \in X$), we must show that $v_*(x_i) = \interpolatedvalues_i$ for $i=1,\dots,\convrank$. We have
	\begin{align*}
		v_*(x_i) &= \constcoeff + \sum_{j=1}^\convrank \secondgreenscoeff_j \secondgreens_j(x_i) \\
		&= \constcoeff + \sum_{j=1}^\convrank \secondgreenscoeff_j \left(\firstgreens_i, \Delta \secondgreens_j\right)_{L^2(\Omega)} + \avg\left(\secondgreens_j\right) \\
		&= \constcoeff + \sum_{j=1}^\convrank \secondgreenscoeff_j \left(\firstgreens_i, \firstgreens_j\right)_{L^2(\Omega)} \\
		&= \constcoeff + \sum_{j=1}^\convrank \secondgreenscoeff_j \pointinteractionmatrix_{ij}
	\end{align*}
	In the first line we used the definition of $v_*$ in \eqref{eq:optimal_v}. In the second line we used Lemma \ref{lem:psi_delta_eval}. In the third line we used the facts that, by construction, $\Delta \secondgreens_j = \firstgreens_j$ and $\int_\Omega \secondgreens_j(x) dx = 0$. In the fourth line we used the definition of $\pointinteractionmatrix$ in \eqref{eq:S_matrix}. Hence the condition $v_*(x_i) = \interpolatedvalues_i$ for $i=1,\dots,\convrank$ may be written in matrix form as
	\begin{equation*}
		\pointinteractionmatrix \bm{\secondgreenscoeff} + \constcoeff \bm{1} = \bm{\interpolatedvalues},
	\end{equation*}
	and this must hold because it is the first block row of system \eqref{eq:interpolation_linear_system} which is solved to compute $\bm{\secondgreenscoeff}$ and $\constcoeff$. So $v_* \in X$.

@@

	\paragraph{Variational equation} To show that $v_*$ satisfies variational equation \eqref{eq:variational_up}, notice that
	\begin{align*}
		(\Delta v_*, \Delta p)_{L^2(\Omega)} =& \sum_{i=1}^\convrank \secondgreenscoeff_i(\Delta \secondgreens_i, \Delta p)_{L^2(\Omega)} \\
		=& \sum_{i=1}^\convrank \secondgreenscoeff_i \left(p(x_i) - \avg\left(p\right)\right) \\
		=& -\avg\left(p\right) \sum_{i=1}^\convrank \secondgreenscoeff_i. 
	\end{align*}
	In the first line we used the definition of $\secondgreens_i$ and the fact that the Laplacian of a constant is zero. In the second line we used Lemma \ref{lem:psi_delta_eval}. In the third line we used the fact that $p(x_i)=0$ because $p \in X_0$. Hence variational equation \eqref{eq:variational_up} holds if $\sum_{i=1}^\convrank \secondgreenscoeff_i = 0$, which may be written in matrix form as $\bm{1}^T \bm{\secondgreenscoeff} = 0$. This must hold because it is the second block row in system \eqref{eq:interpolation_linear_system}.
\end{proof}

@@

		\For{$i=1,2,\dots,\convrank$}{
			Solve the linear system
			\begin{equation*}
			\begin{bmatrix}
			\pointinteractionmatrix & \bm{1} \\ \bm{1}^T & 0
			\end{bmatrix}
			\begin{bmatrix}
			\bm{\secondgreenscoeff}^{(i)} \\ \constcoeff^{(i)}
			\end{bmatrix}
			=
			\begin{bmatrix}
			\bm{e}^{(i)} \\ 0
			\end{bmatrix}.
			\end{equation*}
			for $\bm{\secondgreenscoeff}^{(i)}=(\secondgreenscoeff_1^{(i)}, \secondgreenscoeff_2^{(i)}, \dots, \secondgreenscoeff_\convrank^{(i)})$ and $\constcoeff^{(i)}$. Here $\bm{1} = (1,1,\dots,1) \in \mathbb{R}^\convrank$, and $\bm{e}^{(i)} = (0,\dots,0,1,0,\dots,0)\in \mathbb{R}^\convrank$ is the unit vector with $i^\text{th}$ component equal to one and all other components equal to zero.

			Form the weighting function $w_i$ given by
			\begin{equation*}
			w_i(x) = \constcoeff^{(i)} + \sum_{k=1}^\convrank \secondgreenscoeff_k^{(i)} \secondgreens_k(x).
			\end{equation*}

@@

Replacing $\Aker$ with $\AkerPcMesh$ within the definition of $\Aop$ in \eqref{eq:kernel_representation} yields the following operator approximation, $\AopPcMesh$:
\begin{equation}
	\label{eq:kernel_representation_pcmesh}
	(\AopPcMesh u)(v) := \int_\Omega \int_\Omega v(y) \AkerPcMesh(y,x) u(x) dx dy.
\end{equation}
While $\AopPcMesh$ is well-defined as a mapping $L^2(\Omega) \rightarrow L^2(\Omega)'$, we are interested in the restriction of $\AopPcMesh$ to functions in the finite element space. That is, $\AopPcMesh : V_h \rightarrow V_h'$. Let $u_h \in V_h$ and $v_h \in V_h$, and let $\bm{u}$ and $\bm{v}$ be the coefficient vectors for $u_h$ and $v_h$, respectively, with respect to the finite element basis $\febasis_1, \dots, \febasis_\fedim$. I.e., 
\begin{equation}
	\label{eq:fem_coeff_basis}
	u_h(x) = \sum_{i=1}^\fedim \bm{u}_i \febasis_i(x),
\end{equation}
and similar for $v_h$. Further, let $\bm{M} \in \mathbb{R}^{\fedim \times \fedim}$ be the finite element mass matrix, and let $\AkerPcMat \in \mathbb{R}^{\fedim \times \fedim}$ be following matrix of approximate kernel entries:
\begin{equation}
	\label{eq:Akerpcmat_entries}
	\left(\AkerPcMat\right)_{ij} := \AkerPcMesh(p_i, p_j).
\end{equation}
Using \eqref{eq:defn_of_Akerpcmesh}, \eqref{eq:kernel_representation_pcmesh}, \eqref{eq:fem_coeff_basis}, and \eqref{eq:Akerpcmat_entries}, the definition of the mass matrix, and performing algebraic manipulations, it is straightforward but tedious to show that
\begin{equation*}
	\left(\AopPcMesh u_h \right)(v_h) = \bm{v}^T \bm{M} \AkerPcMat \bm{M} \bm{u}.
\end{equation*}
The finite element matrix representation of $\AopPcMesh$, which we denote by $\AmatPc$, is therefore given by
\begin{equation}
	\label{eq:Amatpc_defn}
	\AmatPc := \bm{M} \AkerPcMat \bm{M}.
\end{equation}

@@

We form an H-matrix representation of $\AmatPc$ by converting $\AkerPcMat$ and $\bm{M}$ to H-matrix format, then using fast H-matrix methods to multiply these matrices according to \eqref{eq:Amatpc_defn}. Once $\AmatPc$ is in H-matrix format, useful matrix operations such as matrix-vector products, matrix-matrix addition, matrix-matrix multiplication, and matrix inversion may be performed using fast scalable H-matrix methods \cite{BORMHACKBUSCHBOOK}. We use H1 matrices in our numerical results, but any of the other H-matrix formats (such as H2, HODLR, HSS, HBS, and others \cite{HMATRIX}) could be used instead. For more details on H-matrices, we recommend \cite{HMATRIXGOOD}.

We convert $\AkerPcMat$ into H1 matrix format using the standard geometrical clustering/adaptive cross method implemented within the HLIBpro software package \cite{HLIBPRO}. Although $\AkerPcMat$ is a dense $\fedim \times \fedim$ matrix, constructing the H-matrix approximation of $\AkerPcMat$ only requires evaluation of $O(\hmatrixrank^2 \fedim \log \fedim)$ entries of $\AkerPc$, and these entries are computed via the formula in Equation \eqref{eq:eval_y_x}. Here $\hmatrixrank$ is the rank of the highest-rank block in the H-matrix. A dense representation of $\AkerPcMat$ is never formed. We describe this H-matrix construction process in detail in Appendix \ref{app:h_matrix}. We convert $\bm{M}$ to H-matrix format using standard H-matrix methods for sparse matrices implemented within HLIBpro, using the same recursive block partitioning structure as was used for $\AkerPcMat$.

@@

After reordering the rows and columns of $\AkerPcMat$ via the depth-first ordering described above, we partition the reordered version of $\AkerPcMat$ into a tree of $2 \times 2$ block matrices recursively. We use a geometric admissibility condition (discussed below) to decide which blocks to subdivide, and use the cluster trees for the rows and columns to determine how to subdivide those blocks. For the first stage of subdivision, let $r_1$ and $r_2$ be the children row clusters for the root of the row cluster tree, let $\colcluster_1$ and $\colcluster_2$ be the children column clusters for the root of the column cluster tree. The matrix $\AkerPcMat$ is partitioned into blocks as follows:
\begin{equation*}
	\begin{bmatrix}
		\left(\AkerPcMat\right)_{11} & \left(\AkerPcMat\right)_{12} \\
		\left(\AkerPcMat\right)_{21} & \left(\AkerPcMat\right)_{22},
	\end{bmatrix}
\end{equation*}
where $\left(\AkerPcMat\right)_{11}$ denotes the block of $\AkerPcMat$ with rows $r_1$ and columns $\colcluster_1$, $\left(\AkerPcMat\right)_{12}$ denotes the block of $\AkerPcMat$ with rows $r_1$ and columns $\colcluster_2$, and so on for $\left(\AkerPcMat\right)_{21}$ and $\left(\AkerPcMat\right)_{22}$.
